---
title: "M9 Project"
author: "Aaron G"
date: "7/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("tidyverse")
library(tidyverse)
auto_accidents <- read_csv("https://data.cityofnewyork.us/resource/h9gi-nx95.csv")
auto_accidents
```

## Auto Accidents

We are working with a data set containing information regarding motor vehicle collisions. In the original dataset, the addresses of where the collisions have occurred were cardinal and not ordinal. In the table below, I have narrowed each address down to the space after each number in order to place the correct suffix at the end. 

```{r cars}
auto_accidents2 <- auto_accidents%>%
  mutate(on_street_name=str_replace(on_street_name,"(?<=1)\\s","st "))%>%
  mutate(on_street_name=str_replace(on_street_name,"(?<=2)\\s","nd "))%>%
  mutate(on_street_name=str_replace(on_street_name,"(?<=3)\\s","rd "))%>%
  mutate(on_street_name=str_replace(on_street_name,"(?<=4)\\s","th "))
auto_accidents2
```


Below, I am attempting to change the street names from all uppercase to normal formatting. This would be the first letter being uppercase and the following to be lower. 

```{r pressure, echo=FALSE}
auto_accidents2%>%
  mutate(on_street_name=str_replace(on_street_name,"([A-Z])(.*)",\L$1$2))
```

I was able to select the first letters and separately the letters after that, but I am no totally sure how to replace the uppercase letters with lowercase ones. 
